---
title: "Watershed Delineation"
author: "Mark Hagemannr"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Assuming you already have the lat-lon of an outlet, computing the contributing watershed is as easy as:

```{r}
ws1 <- delineateWatershed(xlocation = -72.9249, ylocation = 42.3170, crs = 4326, 
                          includeparameters = "true", includeflowtypes = "true")

```

(if timeout is reached before a result is returned, you can specify it using `setTimeout([number of seconds])`)

Here, `crs` is the coordinate reference system number (ESPSG spatial reference code). 

To see what it returned, the `leafletWatershed` function gives a simple interactive map.

```{r}
leafletWatershed(ws1)
```

Other statistics can be found using the `computeChars` (for watershed characteristics such as basin area and land-use) and `computeFlowStats` (for statistics such as flow percentiles)

```{r}
chars1 <- computeChars(workspaceID = ws1$workspaceID, rcode = "MA")
chars1$parameters
```

```{r}
stats1 <- computeFlowStats(workspaceID = ws1$workspaceID, rcode = "MA")
stats1$BANKFULL$flow
```


